\documentclass[11pt, letterpaper]{memoir}
\usepackage{HomeworkStyle}
\geometry{margin=0.75in}



\begin{document}

	\begin{center}
		{\large Quiz 4.1 --	Covalent Bonds}
	\end{center}
	{\large Name: \rule[-1mm]{4in}{.1pt} 


\subsection*{Question 1}
Based on their position on the periodic table, predict how many bonds each element will typically form

{\large \ch{O} \hspace{3em} \ch{Cl} \hspace{3em} \ch{Kr} \hspace{3em} \ch{P} \hspace{3em} \ch{C} \hspace{3em} \ch{F} \hspace{3em} \ch{N} \hspace{3em} \ch{S} \hspace{3em} \ch{He}}

\vspace{1em}
\subsection*{Question 2}
Use Lewis dot diagrams to show how the bonds are formed in the molecules \ch{NH3} and \ch{CO2}

\vspace{3em}
\subsection*{Question 3}
Give the total number of valence electrons in each compound:

{\large \ch{H2O} \hspace{10em} \ch{SF6} \hspace{10em} \ch{CH3COOH}}

\vspace{2em}
\subsection*{Question 4}
Draw a Lewis structure for each compound. Identify sinlge bonds, double bonds, triple bonds, and lone pairs on each structure:

{\large \ch{CH2O} \hspace{10em} \ch{CH3CH3} \hspace{10em} \ch{HCN}}

\vspace{7em}
\subsection*{Question 5}
Draw a Lewis structure and identify which bond is a \emph{coordinate covalent} bond in each compound:

{\large \ch{NH3BF3} \hspace{10em} \ch{NH4^+} \hspace{10em} \ch{N2O}}



\newpage
\newgeometry{margin=1.25in}
\pagestyle{empty}
\addtocounter{page}{-1}
\section*{\emph{Still I Rise}}
\paragraph{By Maya Angelou}~

\vspace{1em}
\begin{minipage}[t]{0.49\linewidth}
	
	You may write me down in history\\
	With your bitter, twisted lies,\\
	You may trod me in the very dirt\\
	But still, like dust, I'll rise.
	
	Does my sassiness upset you?\\
	Why are you beset with gloom?\\
	’Cause I walk like I've got oil wells\\
	Pumping in my living room.
	
	Just like moons and like suns,\\
	With the certainty of tides,\\
	Just like hopes springing high,\\
	Still I'll rise.
	
	Did you want to see me broken?\\
	Bowed head and lowered eyes?\\
	Shoulders falling down like teardrops,\\
	Weakened by my soulful cries?
	
	Does my haughtiness offend you?\\
	Don't you take it awful hard\\
	’Cause I laugh like I've got gold mines\\
	Diggin’ in my own backyard.
	
	You may shoot me with your words,\\
	You may cut me with your eyes,\\
	You may kill me with your hatefulness,\\
	But still, like air, I’ll rise.	
	
\end{minipage}
\begin{minipage}[t]{0.49\linewidth}
	
	Does my sexiness upset you?\\
	Does it come as a surprise\\
	That I dance like I've got diamonds\\
	At the meeting of my thighs?
	
	Out of the huts of history’s shame\\
	I rise\\
	Up from a past that’s rooted in pain\\
	I rise\\
	I'm a black ocean, leaping and wide,\\
	Welling and swelling I bear in the tide.
	
	Leaving behind nights of terror and fear\\
	I rise\\
	Into a daybreak that’s wondrously clear\\
	I rise\\
	Bringing the gifts that my ancestors gave,\\
	I am the dream and the hope of the slave.\\
	I rise\\
	I rise\\
	I rise.	
	
\end{minipage}
\end{document}
